%******************************************************************************
% \file resume_kyle_gieselman.tex
%******************************************************************************

% Variables ------------------------------------------------------------------%
\thispagestyle{empty}



% Configuration --------------------------------------------------------------%

\documentclass[10pt, letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}
\usepackage{enumitem}



% Document -------------------------------------------------------------------%

\begin{document}

%{\fontsize{24}{24}\selectfont Kyle Gieselman} \hfill 2022 \\
\noindent {\bf{\LARGE Kyle Gieselman}} \hfill 2022 \\
gieselman.kyle@gmail.com \\
(317)260-1544 \\
https://www.linkedin.com/in/kylegieselman/ \\
\vspace{-4ex}


%-- SECTION: Summary ---------------------------------------------------------%
\section*{Summary} \vspace{-2ex} \hrule
\vspace{1ex}

Electrical Engineer with 5 years of professional experience in embedded software
(c), software (c++/c\#), schematic capture, and board layout experience. Primarily interested in embedded software positions with a focus on RTOS or bare-metal.

\vspace{-2ex}
%-- SECTION: Experience ------------------------------------------------------%
\section*{Experience} \vspace{-2ex} \hrule
\vspace{1ex}

\subsection*{Vertex}

\textbf{Electrical Engineer II} \hfill December 2021 - Present \\
\vspace{-4ex}
\begin{itemize}[noitemsep]
    \item Common WSI Processor Module \\
    Initiated software design for a Common WSI Processor Module (CWPM). Utilized establish Standard Commands for Programmable Instruments (SCPI) protocol to provide a serial interface to test the board. Trained new hire in embedded systems and common protocols so they could contribute to the effort. Standardized interfaces to promote Agile methodologies and parallel work. Delegated tasks that were thoroughly planned. Reduced risk through use of unit testing with the CppUTest framework.
\end{itemize}


\subsection*{Raytheon}

\textbf{Electrical Engineer II} \hfill July 2019 - December 2021 \\
\vspace{-4ex}
\begin{itemize}[noitemsep]
    \item Maritime Strike Tomahawk Software \\
    Developed low-level drivers and application code using the c language for the power sub-system that was comprised of three separate boards. Spearheaded a migration from SVN to Git to handle the team's version control. This migration also allowed the team to move to an Azure DevOps server with a loose Agile process. Enhanced team's workflow through establishing functional test procedures. Decreased risk by formalizing module design.
    \item AWW-13 Datalink POD Hardware \\
    Expedited schematic design and implemented the printed circuit board layout using Mentor Graphics.
    \item Model Based Design Automation \\
    Developed and delivered scripts for automating printed circuit board documentation in Mentor Graphics. These scripts allowed for documentation inside the design files, moving the company toward model-based design.
    \item David's Sling \\
    Analyzed guidance units due to unexpected errors in production testing. Identified and documented multiple issues that could have been the root cause.
\end{itemize}

\textbf{Electrical Engineer I} \hfill October 2018 - July 2019 \\
\vspace{-4ex}
\begin{itemize}[noitemsep]
    \item Maritime Strike Tomahawk Hardware \\
    Designed the printed circuit board (PCB) for the Power Conditioning Board using Mentor Graphics. This board consisted of multiple rigid sections connect through flexible PCB inner layers.
    \item Documented "green" Gulfstream aircraft using schematics and in-field verification.
\end{itemize}


\textbf{Software Engineer I} \hfill May 2017 - October 2018 \\
\vspace{-4ex}
\begin{itemize}[noitemsep]
    \item HH-60 Personnel Search and Rescue (PRSA) \\
    Developed c++ and c\# code for the Smart Multi-Function Color Displays (SMFCD). Designed updates to incorporate Helmet Mounted Displays (HMD). Attained Raytheon \emph{Six Sigma} certification through reducing man hours and risk when updates were required to configuration files.
    Developed code using c++ and c\#
\end{itemize}


\textbf{Software Engineering Intern} \hfill May 2016 - August 2016 \\
\vspace{-4ex}
\begin{itemize}[noitemsep]
    \item HH-60 Personnel Search and Rescue (PRSA) \\
    Documented functional testing for the Smart Multi-Function Color Displays (SMFCD). Modified c\# code to update the GUI for increased number of menu items.
\end{itemize}


\vspace{-2ex}
%-- SECTION: Education -------------------------------------------------------%
\section*{Education} \vspace{-2ex} \hrule
\vspace{1ex}

\textbf{Valparaiso University} \hfill August 2013 - May 2017 \\
\indent Bachelor of Science in Computer Engineering \\
\indent \indent Graduated Magna Cum Laude \\
\indent \indent Member of \emph{Tau Beta Pi} Honor Society



\end{document}

% eof
